# Data Processing
```{r processing.packages, include=FALSE}
library(tidyverse)
library(lubridate)
library(bookdown)
library(knitr)
```

```{r processing.data, include = F}
data.raw <- read_csv("data/data.1808.csv")
```

## Cleaning Data
The following code performs the following duties:

- Renames variables into user-friendly names 
- Converts character variables with set levels into factors
- Consolidates overlapping levels of factors into one level
- Calculates the scores for the following variables:

  - Substance Dependence Severity (SDS) Scale
  - K6 Psychiatric Inventory (TBC)
  - Dula Dangerous Driving Index (DDDI)
  - State Trait Anger Expression Index (STAXI-2)


```{r processing.clean, message=FALSE, warning=FALSE, cache=TRUE}
data.full <- data.raw[c(-1, -2),] %>% # Remove first two rows (contains description of variables)
  mutate(export_date = today(),
         # Demographics
         drivers_license = as_factor(Q126...13),
         drugs_other_alcohol = as_factor(Q27),
         age = as.numeric(Q19),
         sex = as_factor(Q13),
         ethnicity = fct_recode(as_factor(Q14),
                                "Eastern European" = "Southern and Eastern European (e.g. Albania, Bosnia and Herzegovina, Bulgaria, Croatia, Greece)",
                                "Oceanian"= "Oceanian (Australian, Aboriginal, Torres Strait Islander)",
                                "Undisclosed" = "Prefer not to say",
                                "North-West European" = "North-West European (e.g.  UK, Ireland, France, Germany, Spain, Belgium, Portugal, Austria, Andorra, Czechia)",
                                "Central Asian" = "Southern and Central Asian (e.g. Afghanistan, Bangladesh, Bhutan, India, Kyrgyzstan, Kazakhstan, Maldives, Nepal, Pakistan, Sri Lanka)",
                                "Asian" = "North-East Asian (e.g. China, Japan, North Korea, South Korea, Mongolia)",
                                "American" = "People of the Americas (e.g. indigenous peoples of the Americas are the pre-Columbian peoples of North, Central and South America)",
                                "Middle-East" = "North African and Middle Eastern (e.g. Egypt, and Turkey)",
                                "South-East Asian" = "South-East Asian (e.g. Cambodia, Indonesia, Laos, Malaysia, the Philippines, Singapore, Thailand and Vietnam)",
                                "African" = "Sub-Saharan African (e.g. Botswana,Cameroon, Central African Republic, Congo, Ethiopia, Ghana, Guinea, Kenya, Liberia, Namibia, Nigeria)"
         ),
         marital_status = as_factor(Q15),
         education = fct_recode(as_factor(Q20),
                                "Did not finish high school" = "Attended high school but did not finish",
                                "High School Diploma" = "High School Diploma",
                                "Vocational/Technical degree or certificate" = "Vocational/Technical degree or certificate",
                                "Did not finish University" = "Attended University but did not finish",
                                "Bachelor Degree" = "Bachelor Degree",
                                "Postgraduate Degree" = "Master’s Degree",
                                "Postgraduate Degree" = "Postgraduate Degree"
         ),
         employment_status = as_factor(Q17),
         area_live = as_factor(Q21),
         license_status = as_factor(Q22),
         # Alcohol Use
         alcohol_ever = as_factor(Q28),
         alcohol_past_12_least_12 = as_factor(Q29),
         alcohol_frequency = as_factor(Q33...40),
         alcohol_consumption = as_factor(Q31),
         alcohol_six_or_more = as_factor(Q32),
         # Drug Use
         drug_use_cocaine = fct_recode(as_factor(Q63_1),
                                       "Never" = "Neither/not used",
                                       "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                       "Past 12 months" = "PAST 12 MONTHS",
                                       "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_cannabis = fct_recode(as_factor(Q63_2),
                                        "Never" = "Neither/not used",
                                        "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                        "Past 12 months" = "PAST 12 MONTHS",
                                        "Past 12 months" = "PAST 12 MONTHS,Neither/not used",
                                        "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_club_drugs = fct_recode(as_factor(Q63_3),
                                          "Never" = "Neither/not used",
                                          "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                          "Past 12 months" = "PAST 12 MONTHS",
                                          "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_hallucinogens = fct_recode(as_factor(Q63_4),
                                             "Never" = "Neither/not used",
                                             "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                             "Before 12 months" = "BEFORE 12 MONTHS AGO,Neither/not used",
                                             "Past 12 months" = "PAST 12 MONTHS",
                                             "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_inhalants = fct_recode(as_factor(Q63_5),
                                         "Never" = "Neither/not used",
                                         "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                         "Past 12 months" = "PAST 12 MONTHS",
                                         "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_heroin = fct_recode(as_factor(Q63_6),
                                      "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                      "Never" = "Neither/not used",
                                      "Past 12 months" = "PAST 12 MONTHS"
         ),
         drug_use_sedatives = fct_recode(as_factor(Q63_7),
                                         "Never" = "Neither/not used",
                                         "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                         "Past 12 months" = "PAST 12 MONTHS",
                                         "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         drug_use_new_psychoactive = fct_recode(as_factor(Q63_8),
                                                "Never" = "Neither/not used",
                                                "Before 12 months" = "BEFORE 12 MONTHS AGO",
                                                "Before 12 months" = "BEFORE 12 MONTHS AGO,Neither/not used",
                                                "Past 12 months" = "PAST 12 MONTHS",
                                                "Both" = "PAST 12 MONTHS,BEFORE 12 MONTHS AGO"
         ),
         prescription_drugs = as_factor(Q64),
         prescription_drug_use = as_factor(Q144), # Will need to consolidate levels
         pres_use_pain_killer_pres = as_factor(Q125_1), # Off-label prescription drug use, prescription pain killer
         pres_use_pain_killer_otc = as_factor(Q125_2), # Off-label prescription drug use, over the counter
         pres_use_sleeping_pill = as_factor(Q125_3),
         pres_use_methadone = as_factor(Q125_4),
         pres_use_ritalin = as_factor(Q125_5),
         # MA use
         meth_ingest = as_factor(Q47),
         meth_most_common = as_factor(Q48),
         meth_use_at_peak = as_factor(Q49),
         meth_last_12_months = as_factor(Q50),
         meth_before_last_year = as_factor(Q51),
         meth_recent_use = as_factor(Q52),
         meth_use_age = fct_recode(as_factor(Q53),
                                   "25" = "25 years old."),
         meth_use_ways = Q54, # Think about how to organise factors
         ## SDS Scale (Re-scored to not use zero as R is weird with zeros)
         meth_out_of_control = as.numeric(fct_recode(as_factor(Q55),
                                                     "1" = "Never or almost never",
                                                     "2" = "Sometimes",
                                                     "3" = "Often",
                                                     "4" = "Always")
         ),
         meth_anxious_about_missing = as.numeric(fct_recode(as_factor(Q56),
                                                            "1" = "Never or almost never",
                                                            "2" = "Sometimes",
                                                            "3" = "Often",
                                                            "4" = "Always")
         ),
         meth_worry_about_use = as.numeric(fct_recode(as_factor(Q57),
                                                      "1" = "Not at all",
                                                      "2" = "A little",
                                                      "3" = "Often",
                                                      "4" = "Always or nearly always")
         ),
         meth_wish_stop = as.numeric(fct_recode(as_factor(Q58),
                                                "1" = "Never or almost never",
                                                "2" = "Sometimes",
                                                "3" = "Often",
                                                "4" = "Always")
         ),
         meth_difficulty_stopping = as.numeric(fct_recode(as_factor(Q60),
                                                          "1" = "Not difficult at all",
                                                          "2" = "Quite difficult",
                                                          "3" = "Very difficult",
                                                          "4" = "Impossible")
         ),
         meth_SDS = ((meth_out_of_control - 1) + (meth_anxious_about_missing - 1) + (meth_worry_about_use - 1) + 
                  (meth_wish_stop - 1) + (meth_difficulty_stopping - 1)),
         meth_user = ifelse(meth_SDS > 4, "MUD", "Recreational"),
         meth_want_to_change = as_factor(Q61),
         meth_could_change = as_factor(Q62),
         # K6 Distress scale
         k6_nervous = as_factor(Q33...58),
         k6_hopeless = as_factor(Q34),
         k6_restless = as_factor(Q35),
         k6_depressed = as_factor(Q44),
         k6_effort = as_factor(Q36),
         k6_worthless = as_factor(Q37),
         k6_physical_cause = as_factor(Q43),
         # Add psychiatric diagnoses (consolidate levels)
         psychiatric_diagnoses = fct_recode(as_factor(Q46), # I think it might be best to have separate columns for each diagnosis.
                                            "Major Depressive Disorder" = "Major Depressive Disorder (MDD)",
                                            "Bipolar Disorder" = "Bipolar I Disorder",
                                            "Bipolar Disorder" = "Bipolar II Disorder",
                                            "Eating Disorder" = "Anorexia Nervosa",
                                            "Eating Disorder" = "Binge-eating disorder",
                                            "Eating Disorder" = "Bulimia Nervosa",
                                            "Personality Disorder" = "Borderline Personality Disorder (BPD)",
                                            "PTSD" = "Post Traumatic Stress Disorder (PTSD)",
                                            "Attention Deficit Disorder" = "Attention Deficit Disorder (ADD)",
                                            "Attention Deficit Disorder" = "Attention Deficit Hyperactivity Disorder (ADHD)"
         ),
         # Instances Driving Under Influence of Alcohol (DUI)
         DUI_suspended = as_factor(Q95),
         DUI_hurt = as_factor(Q96),
         # Attitudes toward Drink Driving
         DUI_attitude_friends = as.numeric(fct_recode(as_factor(Q97), # Reverse coded
                                                      "1" = "Strongly disagree",
                                                      "2" = "Disagree",
                                                      "3" = "Somewhat disagree",
                                                      "4" = "Neither agree nor disagree",
                                                      "5" = "Somewhat agree",
                                                      "6" = "Agree",
                                                      "7" = "Strongly Agree")
         ),
         DUI_attitude_drunk = as.numeric(fct_recode(as_factor(Q98), # Reverse coded
                                                    "1" = "Strongly disagree",
                                                    "2" = "Disagree",
                                                    "3" = "Somewhat disagree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat agree",
                                                    "6" = "Agree",
                                                    "7" = "Strongly Agree")
         ),
         DUI_attitude_jail = as.numeric(fct_recode(as_factor(Q99),
                                                   "1" = "Strongly Agree",
                                                   "2" = "Agree",
                                                   "3" = "Somewhat agree",
                                                   "4" = "Neither agree nor disagree",
                                                   "5" = "Somewhat disagree",
                                                   "6" = "Disagree",
                                                   "7" = "Strongly disagree")
         ),
         DUI_attitude_strict = as.numeric(fct_recode(as_factor(Q100),
                                                     "1" = "Strongly Agree",
                                                     "2" = "Agree",
                                                     "3" = "Somewhat agree",
                                                     "4" = "Neither agree nor disagree",
                                                     "5" = "Somewhat disagree",
                                                     "6" = "Disagree",
                                                     "7" = "Strongly disagree")
         ),
         DUI_attitude_tough = as.numeric(fct_recode(as_factor(Q101),
                                                    "1" = "Strongly Agree",
                                                    "2" = "Agree",
                                                    "3" = "Somewhat agree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat disagree",
                                                    "6" = "Disagree",
                                                    "7" = "Strongly disagree")
         ),
         DUI_attitude_caught = as.numeric(fct_recode(as_factor(Q102), # Reverse coded
                                                      "1" = "Strongly disagree",
                                                      "2" = "Disagree",
                                                      "3" = "Somewhat disagree",
                                                      "4" = "Neither agree nor disagree",
                                                      "5" = "Somewhat agree",
                                                      "6" = "Agree",
                                                      "7" = "Strongly Agree")
         ),
         DUI_attitude_while = as.numeric(fct_recode(as_factor(Q103), # Reverse coded
                                                     "1" = "Strongly disagree",
                                                     "2" = "Disagree",
                                                     "3" = "Somewhat disagree",
                                                     "4" = "Neither agree nor disagree",
                                                     "5" = "Somewhat agree",
                                                     "6" = "Agree",
                                                     "7" = "Strongly Agree")
         ),
         DUI_attitude_dumb = as.numeric(fct_recode(as_factor(Q104),
                                                    "1" = "Strongly Agree",
                                                    "2" = "Agree",
                                                    "3" = "Somewhat agree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat disagree",
                                                    "6" = "Disagree",
                                                    "7" = "Strongly disagree")
         ),
         DUI_attitude_overrated = as.numeric(fct_recode(as_factor(Q105), # Reverse coded
                                                         "1" = "Strongly disagree",
                                                         "2" = "Disagree",
                                                         "3" = "Somewhat disagree",
                                                         "4" = "Neither agree nor disagree",
                                                         "5" = "Somewhat agree",
                                                         "6" = "Agree",
                                                         "7" = "Strongly Agree")
         ),
         DUI_attitude_license = as.numeric(fct_recode(as_factor(Q106),
                                                       "1" = "Strongly Agree",
                                                       "2" = "Agree",
                                                       "3" = "Somewhat agree",
                                                       "4" = "Neither agree nor disagree",
                                                       "5" = "Somewhat disagree",
                                                       "6" = "Disagree",
                                                       "7" = "Strongly disagree")
         ),
         # Attitudes towards strategies for avoiding Drink Driving: Discrete
         DUI_strategy_leave = as.numeric(fct_recode(as_factor(Q107),
                                                     "1" = "Definitely yes",
                                                     "2" = "Probably yes",
                                                     "3" = "Might or might not",
                                                     "4" = "Probably not",
                                                     "5" = "Definitely not")
         ),
         DUI_strategy_light = as.numeric(fct_recode(as_factor(Q108),
                                                    "1" = "Extremely likely",
                                                    "2" = "Moderately likely",
                                                    "2" = "Slightly likely",
                                                    "3" = "Neither likely nor unlikely",
                                                    "4" = "Slightly unlikely",
                                                    "4" = "Moderately unlikely",
                                                    "5" = "Extremely unlikely")
         ),
         DUI_strategy_plan_driver = as.numeric(fct_recode(as_factor(Q109),
                                                           "1" = "Extremely likely",
                                                           "2" = "Moderately likely",
                                                           "2" = "Slightly likely",
                                                           "3" = "Neither likely nor unlikely",
                                                           "4" = "Slightly unlikely",
                                                           "4" = "Moderately unlikely",
                                                           "5" = "Extremely unlikely")
         ),
         DUI_strategy_plan_use = as.numeric(fct_recode(as_factor(Q110),
                                                        "1" = "Extremely likely",
                                                        "2" = "Moderately likely",
                                                        "2" = "Slightly likely",
                                                        "3" = "Neither likely nor unlikely",
                                                        "4" = "Slightly unlikely",
                                                        "4" = "Moderately unlikely",
                                                        "5" = "Extremely unlikely")
         ),
         DUI_strategy_taxi = as.numeric(fct_recode(as_factor(Q111),
                                                    "1" = "Extremely likely",
                                                    "2" = "Moderately likely",
                                                    "2" = "Slightly likely",
                                                    "3" = "Neither likely nor unlikely",
                                                    "4" = "Slightly unlikely",
                                                    "4" = "Moderately unlikely",
                                                    "5" = "Extremely unlikely")
         ),
         DUI_strategy_track = as.numeric(fct_recode(as_factor(Q112),
                                                     "1" = "Extremely likely",
                                                     "2" = "Moderately likely",
                                                     "2" = "Slightly likely",
                                                     "3" = "Neither likely nor unlikely",
                                                     "4" = "Slightly unlikely",
                                                     "4" = "Moderately unlikely",
                                                     "5" = "Extremely unlikely")
         ),
         DUI_strategy_overnight = as.numeric(fct_recode(as_factor(Q113),
                                                         "1" = "Extremely likely",
                                                         "2" = "Moderately likely",
                                                         "2" = "Slightly likely",
                                                         "3" = "Neither likely nor unlikely",
                                                         "4" = "Slightly unlikely",
                                                         "4" = "Moderately unlikely",
                                                         "5" = "Extremely unlikely")
         ),
         # Attitudes towards strategies for avoiding Drink Driving: Dichotomous
         DUI_strategy_leave_dich = as.numeric(fct_recode(as_factor(Q107),
                                                    "agree" = "Definitely yes",
                                                    "agree" = "Probably yes",
                                                    "disagree" = "Might or might not",
                                                    "disagree" = "Probably not",
                                                    "disagree" = "Definitely not")
         ),
         DUI_strategy_light_dich = as.numeric(fct_recode(as_factor(Q108),
                                                    "agree" = "Extremely likely",
                                                    "agree" = "Moderately likely",
                                                    "agree" = "Slightly likely",
                                                    "disagree" = "Neither likely nor unlikely",
                                                    "disagree" = "Slightly unlikely",
                                                    "disagree" = "Moderately unlikely",
                                                    "disagree" = "Extremely unlikely")
         ),
         DUI_strategy_plan_driver_dich = as.numeric(fct_recode(as_factor(Q109),
                                                               "agree" = "Extremely likely",
                                                               "agree" = "Moderately likely",
                                                               "agree" = "Slightly likely",
                                                               "disagree" = "Neither likely nor unlikely",
                                                               "disagree" = "Slightly unlikely",
                                                               "disagree" = "Moderately unlikely",
                                                               "disagree" = "Extremely unlikely")
         ),
         DUI_strategy_plan_use_dich = as.numeric(fct_recode(as_factor(Q110),
                                                            "agree" = "Extremely likely",
                                                            "agree" = "Moderately likely",
                                                            "agree" = "Slightly likely",
                                                            "disagree" = "Neither likely nor unlikely",
                                                            "disagree" = "Slightly unlikely",
                                                            "disagree" = "Moderately unlikely",
                                                            "disagree" = "Extremely unlikely")
         ),
         DUI_strategy_taxi_dich = as.numeric(fct_recode(as_factor(Q111),
                                                        "agree" = "Extremely likely",
                                                        "agree" = "Moderately likely",
                                                        "agree" = "Slightly likely",
                                                        "disagree" = "Neither likely nor unlikely",
                                                        "disagree" = "Slightly unlikely",
                                                        "disagree" = "Moderately unlikely",
                                                        "disagree" = "Extremely unlikely")
         ),
         DUI_strategy_track_dich = as.numeric(fct_recode(as_factor(Q112),
                                                    "agree" = "Extremely likely",
                                                    "agree" = "Moderately likely",
                                                    "agree" = "Slightly likely",
                                                    "disagree" = "Neither likely nor unlikely",
                                                    "disagree" = "Slightly unlikely",
                                                    "disagree" = "Moderately unlikely",
                                                    "disagree" = "Extremely unlikely")
         ),
         DUI_strategy_overnight_dich = as.numeric(fct_recode(as_factor(Q113),
                                                             "agree" = "Extremely likely",
                                                             "agree" = "Moderately likely",
                                                             "agree" = "Slightly likely",
                                                             "disagree" = "Neither likely nor unlikely",
                                                             "disagree" = "Slightly unlikely",
                                                             "disagree" = "Moderately unlikely",
                                                             "disagree" = "Extremely unlikely")
         ),
         # Instances Driving Under Influence of Drugs (DUID)
         DUID_incidence = as_factor(Q114),
         DUID_recent = as_factor(Q118),
         DUID_recent_drugs = fct_recode(as_factor(Q119), # Should Consolidate levels in a better way
                                        "Amphetamine only" = "Amphetamine",
                                        "Cocaine only" = "Cocaine",
                                        "Marijuana only" = "Marijuana/Cannabis",
                                        "Club drugs only" = "Club drugs (e.g ketamine, GHB)",
                                        "Hallucinogens only" = "Hallucinogens/psychedelics (e.g acid, LSD, DMT)",
                                        "Sedatives only" = "Sedatives/tranquilisers (e.g. Xanax, Valium)"
         ),
         DUID_lifetime = as_factor(Q120),
         DUID_lifetime_drugs = Q121, # Consolidate levels
         DUID_ongoing = as_factor(ifelse(DUID_recent == "Yes" & DUID_lifetime == "Yes", "Yes", "No")),
         DUID_suspended = as_factor(Q122),
         DUID_suspended_drugs = Q124, # Consolidate levels
         DUID_hurt = as_factor(Q123),
         DUID_hurt_drugs = as_factor(Q125),
         # Attitudes toward Drug Driving
         DUID_attitude_friends = as.numeric(fct_recode(as_factor(Q126...75), # Reverse coded
                                                       "1" = "Strongly disagree",
                                                       "2" = "Disagree",
                                                       "3" = "Somewhat disagree",
                                                       "4" = "Neither agree nor disagree",
                                                       "5" = "Somewhat agree",
                                                       "6" = "Agree",
                                                       "7" = "Strongly agree")
         ),
         DUID_attitude_high = as.numeric(fct_recode(as_factor(Q128), # Reverse coded
                                                    "1" = "Strongly disagree",
                                                    "2" = "Disagree",
                                                    "3" = "Somewhat disagree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat agree",
                                                    "6" = "Agree",
                                                    "7" = "Strongly agree")
         ),
         DUID_attitude_jail = as.numeric(fct_recode(as_factor(Q129),
                                                    "1" = "Strongly agree",
                                                    "2" = "Agree",
                                                    "3" = "Somewhat agree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat disagree",
                                                    "6" = "Disagree",
                                                    "7" = "Strongly disagree")
         ),
         DUID_attitude_strict = as.numeric(fct_recode(as_factor(Q130),
                                                      "1" = "Strongly agree",
                                                      "2" = "Agree",
                                                      "3" = "Somewhat agree",
                                                      "4" = "Neither agree nor disagree",
                                                      "5" = "Somewhat disagree",
                                                      "6" = "Disagree",
                                                      "7" = "Strongly disagree")
         ),
         DUID_attitude_tough = as.numeric(fct_recode(as_factor(Q131),
                                                     "1" = "Strongly agree",
                                                     "2" = "Agree",
                                                     "3" = "Somewhat agree",
                                                     "4" = "Neither agree nor disagree",
                                                     "5" = "Somewhat disagree",
                                                     "6" = "Disagree",
                                                     "7" = "Strongly disagree")
         ),
         DUID_attitude_caught = as.numeric(fct_recode(as_factor(Q132), # Reverse coded
                                                      "1" = "Strongly disagree",
                                                      "2" = "Disagree",
                                                      "3" = "Somewhat disagree",
                                                      "4" = "Neither agree nor disagree",
                                                      "5" = "Somewhat agree",
                                                      "6" = "Agree",
                                                      "7" = "Strongly agree")
         ),
         DUID_attitude_while = as.numeric(fct_recode(as_factor(Q133), # Reverse coded
                                                     "1" = "Strongly disagree",
                                                     "2" = "Disagree",
                                                     "3" = "Somewhat disagree",
                                                     "4" = "Neither agree nor disagree",
                                                     "5" = "Somewhat agree",
                                                     "6" = "Agree",
                                                     "7" = "Strongly agree")
         ),
         DUID_attitude_dumb = as.numeric(fct_recode(as_factor(Q134),
                                                    "1" = "Strongly agree",
                                                    "2" = "Agree",
                                                    "3" = "Somewhat agree",
                                                    "4" = "Neither agree nor disagree",
                                                    "5" = "Somewhat disagree",
                                                    "6" = "Disagree",
                                                    "7" = "Strongly disagree")
         ),
         DUID_attitude_overrated = as.numeric(fct_recode(as_factor(Q135), # Reverse coded
                                                         "1" = "Strongly disagree",
                                                         "2" = "Disagree",
                                                         "3" = "Somewhat disagree",
                                                         "4" = "Neither agree nor disagree",
                                                         "5" = "Somewhat agree",
                                                         "6" = "Agree",
                                                         "7" = "Strongly agree")
         ),
         DUID_attitude_license = as.numeric(fct_recode(as_factor(Q136),
                                                       "1" = "Strongly agree",
                                                       "2" = "Agree",
                                                       "3" = "Somewhat agree",
                                                       "4" = "Neither agree nor disagree",
                                                       "5" = "Somewhat disagree",
                                                       "6" = "Disagree",
                                                       "7" = "Strongly disagree")
         ),
         # Attitudes towards strategies for avoiding Drug Driving: Discrete
         DUID_strategy_leave = as.numeric(fct_recode(as_factor(Q137),
                                                     "1" = "Definitely yes",
                                                     "2" = "Probably yes",
                                                     "3" = "Might or might not",
                                                     "4" = "Probably not",
                                                     "5" = "Definitely not")
         ),
         DUID_strategy_less = as.numeric(fct_recode(as_factor(Q138),
                                                    "1" = "Extremely likely",
                                                    "2" = "Moderately likely",
                                                    "2" = "Slightly likely",
                                                    "3" = "Neither likely nor unlikely",
                                                    "4" = "Slightly unlikely",
                                                    "4" = "Moderately unlikely",
                                                    "5" = "Extremely unlikely")
         ),
         DUID_strategy_plan_driver = as.numeric(fct_recode(as_factor(Q139),
                                                           "1" = "Extremely likely",
                                                           "2" = "Moderately likely",
                                                           "2" = "Slightly likely",
                                                           "3" = "Neither likely nor unlikely",
                                                           "4" = "Slightly unlikely",
                                                           "4" = "Moderately unlikely",
                                                           "5" = "Extremely unlikely")
         ),
         DUID_strategy_plan_use = as.numeric(fct_recode(as_factor(Q140),
                                                        "1" = "Extremely likely",
                                                        "2" = "Moderately likely",
                                                        "2" = "Slightly likely",
                                                        "3" = "Neither likely nor unlikely",
                                                        "4" = "Slightly unlikely",
                                                        "4" = "Moderately unlikely",
                                                        "5" = "Extremely unlikely")
         ),
         DUID_strategy_taxi = as.numeric(fct_recode(as_factor(Q141),
                                                    "1" = "Extremely likely",
                                                    "2" = "Moderately likely",
                                                    "2" = "Slightly likely",
                                                    "3" = "Neither likely nor unlikely",
                                                    "4" = "Slightly unlikely",
                                                    "4" = "Moderately unlikely",
                                                    "5" = "Extremely unlikely")
         ),
         DUID_strategy_track = as.numeric(fct_recode(as_factor(Q142),
                                                     "1" = "Extremely likely",
                                                     "2" = "Moderately likely",
                                                     "2" = "Slightly likely",
                                                     "3" = "Neither likely nor unlikely",
                                                     "4" = "Slightly unlikely",
                                                     "4" = "Moderately unlikely",
                                                     "5" = "Extremely unlikely")
         ),
         DUID_strategy_overnight = as.numeric(fct_recode(as_factor(Q143),
                                                         "1" = "Extremely likely",
                                                         "2" = "Moderately likely",
                                                         "2" = "Slightly likely",
                                                         "3" = "Neither likely nor unlikely",
                                                         "4" = "Slightly unlikely",
                                                         "4" = "Moderately unlikely",
                                                         "5" = "Extremely unlikely")
         ),
         # Attitudes towards strategies for avoiding Drug Driving: Dichotomous
         DUID_strategy_leave_dich = as.numeric(fct_recode(as_factor(Q137),
                                                     "agree" = "Definitely yes",
                                                     "agree" = "Probably yes",
                                                     "disagree" = "Might or might not",
                                                     "disagree" = "Probably not",
                                                     "disagree" = "Definitely not")
         ),
         DUID_strategy_less = as.numeric(fct_recode(as_factor(Q138),
                                                    "agree" = "Extremely likely",
                                                    "agree" = "Moderately likely",
                                                    "agree" = "Slightly likely",
                                                    "disagree" = "Neither likely nor unlikely",
                                                    "disagree" = "Slightly unlikely",
                                                    "disagree" = "Moderately unlikely",
                                                    "disagree" = "Extremely unlikely")
         ),
         DUID_strategy_plan_driver = as.numeric(fct_recode(as_factor(Q139),
                                                           "agree" = "Extremely likely",
                                                           "agree" = "Moderately likely",
                                                           "agree" = "Slightly likely",
                                                           "disagree" = "Neither likely nor unlikely",
                                                           "disagree" = "Slightly unlikely",
                                                           "disagree" = "Moderately unlikely",
                                                           "disagree" = "Extremely unlikely")
         ),
         DUID_strategy_plan_use = as.numeric(fct_recode(as_factor(Q140),
                                                        "agree" = "Extremely likely",
                                                        "agree" = "Moderately likely",
                                                        "agree" = "Slightly likely",
                                                        "disagree" = "Neither likely nor unlikely",
                                                        "disagree" = "Slightly unlikely",
                                                        "disagree" = "Moderately unlikely",
                                                        "disagree" = "Extremely unlikely")
         ),
         DUID_strategy_taxi = as.numeric(fct_recode(as_factor(Q141),
                                                    "agree" = "Extremely likely",
                                                    "agree" = "Moderately likely",
                                                    "agree" = "Slightly likely",
                                                    "disagree" = "Neither likely nor unlikely",
                                                    "disagree" = "Slightly unlikely",
                                                    "disagree" = "Moderately unlikely",
                                                    "disagree" = "Extremely unlikely")
         ),
         DUID_strategy_track = as.numeric(fct_recode(as_factor(Q142),
                                                     "agree" = "Extremely likely",
                                                     "agree" = "Moderately likely",
                                                     "agree" = "Slightly likely",
                                                     "disagree" = "Neither likely nor unlikely",
                                                     "disagree" = "Slightly unlikely",
                                                     "disagree" = "Moderately unlikely",
                                                     "disagree" = "Extremely unlikely")
         ),
         DUID_strategy_overnight = as.numeric(fct_recode(as_factor(Q143),
                                                         "agree" = "Extremely likely",
                                                         "agree" = "Moderately likely",
                                                         "agree" = "Slightly likely",
                                                         "disagree" = "Neither likely nor unlikely",
                                                         "disagree" = "Slightly unlikely",
                                                         "disagree" = "Moderately unlikely",
                                                         "disagree" = "Extremely unlikely")
         ),
         # Dula Dangerous Driving Index (DDDI)
         DDDI_NE_1 = as.numeric(fct_recode(as_factor(Q65),
                                "1" = "Never",
                                "2" = "Rarely",
                                "3" = "Sometimes",
                                "4" = "Often",
                                "5" = "Always")
         ),
         DDDI_NE_2 = as.numeric(fct_recode(as_factor(Q66),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_3 = as.numeric(fct_recode(as_factor(Q67),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_1 = as.numeric(fct_recode(as_factor(Q68),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_2 = as.numeric(fct_recode(as_factor(Q69),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_3 = as.numeric(fct_recode(as_factor(Q70),
                                          "1" = "Never",
                                          "2" = "Rarely",
                                          "3" = "Sometimes",
                                          "4" = "Often",
                                          "5" = "Always")
         ),
         DDDI_AD_4 = as.numeric(fct_recode(as_factor(Q73),
                                          "1" = "Never",
                                          "2" = "Rarely",
                                          "3" = "Sometimes",
                                          "4" = "Often",
                                          "5" = "Always")
         ),
         DDDI_RD_1 = as.numeric(fct_recode(as_factor(Q74),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_5 = as.numeric(fct_recode(as_factor(Q75),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_2 = as.numeric(fct_recode(as_factor(Q76),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_6 = as.numeric(fct_recode(as_factor(Q77),
                                         "1" = "Never",
                                         "2" = "Rarely",
                                         "3" = "Sometimes",
                                         "4" = "Often",
                                         "5" = "Always")
         ),
         DDDI_NE_4 = as.numeric(fct_recode(as_factor(Q79),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_3 = as.numeric(fct_recode(as_factor(Q80),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_4 = as.numeric(fct_recode(as_factor(Q81),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_AD_7 = as.numeric(fct_recode(as_factor(Q82),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_5 = as.numeric(fct_recode(as_factor(Q83),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_6 = as.numeric(fct_recode(as_factor(Q84),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_7 = as.numeric(fct_recode(as_factor(Q85),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_5 = as.numeric(fct_recode(as_factor(Q86),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_6 = as.numeric(fct_recode(as_factor(Q87),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_8 = as.numeric(fct_recode(as_factor(Q88),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_7 = as.numeric(fct_recode(as_factor(Q89),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_8 = as.numeric(fct_recode(as_factor(Q90),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_9 = as.numeric(fct_recode(as_factor(Q91),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_NE_9 = as.numeric(fct_recode(as_factor(Q92),
                                           "1" = "Never",
                                           "2" = "Rarely",
                                           "3" = "Sometimes",
                                           "4" = "Often",
                                           "5" = "Always")
         ),
         DDDI_RD_10 = as.numeric(fct_recode(as_factor(Q93),
                                            "1" = "Never",
                                            "2" = "Rarely",
                                            "3" = "Sometimes",
                                            "4" = "Often",
                                            "5" = "Always")
         ),
         DDDI_RD_11 = as.numeric(fct_recode(as_factor(Q94),
                                            "1" = "Never",
                                            "2" = "Rarely",
                                            "3" = "Sometimes",
                                            "4" = "Often",
                                            "5" = "Always")
         ),
         ## DDDI summing up scores
         DDDI_NE_Total = (DDDI_NE_1 + DDDI_NE_2 + DDDI_NE_3 + DDDI_NE_4 + DDDI_NE_5 + DDDI_NE_6 + DDDI_NE_7 + DDDI_NE_8 + DDDI_NE_9), # Negative Emotions
         DDDI_AD_Total = (DDDI_AD_1 + DDDI_AD_2 + DDDI_AD_3 + DDDI_AD_4 + DDDI_AD_5 + DDDI_AD_6 + DDDI_AD_7), # Agressive Driving
         DDDI_RD_Total = (DDDI_RD_1 + DDDI_RD_2 + DDDI_RD_3 + DDDI_RD_4 + DDDI_RD_5 + DDDI_RD_6 + DDDI_RD_7 + DDDI_RD_8 + DDDI_RD_9 + DDDI_RD_10 + DDDI_RD_11), # Risky Driving
         DDDI_Total = (DDDI_NE_Total + DDDI_AD_Total + DDDI_RD_Total),
         keep_DDDI = !is.na(DDDI_Total), # Logical to indicate whether DDDI has been completed
         # STAXI - 2
         ## State Anger
         S_Ang_F_1 = as.numeric(fct_recode(as_factor(Q146_1),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_F_2 = as.numeric(fct_recode(as_factor(Q146_2),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_F_3 = as.numeric(fct_recode(as_factor(Q146_3),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_V_1 = as.numeric(fct_recode(as_factor(Q146_4),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_P_1 = as.numeric(fct_recode(as_factor(Q146_5),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_F_4 = as.numeric(fct_recode(as_factor(Q146_6),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_P_2 = as.numeric(fct_recode(as_factor(Q146_7),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_P_3 = as.numeric(fct_recode(as_factor(Q146_8),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_V_2 = as.numeric(fct_recode(as_factor(Q146_9),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_F_5 = as.numeric(fct_recode(as_factor(Q146_10),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_P_4 = as.numeric(fct_recode(as_factor(Q146_11),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_V_3 = as.numeric(fct_recode(as_factor(Q146_12),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_V_4 = as.numeric(fct_recode(as_factor(Q146_13),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_P_5 = as.numeric(fct_recode(as_factor(Q146_14),
                                           "1" = "Not at all",
                                           "2" = "Somewhat",
                                           "3" = "Moderately so",
                                           "4" = "Very much so")
         ),
         S_Ang_F_Total = (S_Ang_F_1 + S_Ang_F_2 + S_Ang_F_3 + S_Ang_F_4 + S_Ang_F_5),
         S_Ang_P_Total = (S_Ang_P_1 + S_Ang_P_2 + S_Ang_P_3 + S_Ang_P_4 + S_Ang_P_5),
         S_Ang_V_Total = (S_Ang_V_1 + S_Ang_V_2 + S_Ang_V_3 + S_Ang_V_4), 
         S_Ang_Total = (S_Ang_F_1 + S_Ang_F_2 + S_Ang_F_3 + S_Ang_F_4 + S_Ang_F_5 + 
                          S_Ang_P_1 + S_Ang_P_2 + S_Ang_P_3 + S_Ang_P_4 + S_Ang_P_5 +
                          S_Ang_V_1 + S_Ang_V_2 + S_Ang_V_3 + S_Ang_V_4),
         ## Trait Anger
         T_Ang_T_1 = as.numeric(fct_recode(as_factor(Q147_1),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "4" = "Almost always")
         ),
         T_Ang_T_2 = as.numeric(fct_recode(as_factor(Q147_2),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Sometimes,Often",
                                           "4" = "Almost always")
         ),
         T_Ang_T_3 = as.numeric(fct_recode(as_factor(Q147_3),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Sometimes,Often",
                                           "3" = "Almost never,Often",
                                           "4" = "Almost always",
                                           "4" = "Sometimes,Often,Almost always")
         ),
         T_Ang_R_1 = as.numeric(fct_recode(as_factor(Q147_4),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Sometimes,Often",
                                           "4" = "Almost always")
         ),
         T_Ang_R_2 = as.numeric(fct_recode(as_factor(Q147_5),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Almost never,Sometimes,Often",
                                           "4" = "Almost always")
         ),
         T_Ang_T_4 = as.numeric(fct_recode(as_factor(Q147_6),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "4" = "Almost always",
                                           "4" = "Often,Almost always")
         ),
         T_Ang_1 = as.numeric(fct_recode(as_factor(Q147_7),
                                         "1" = "Almost never",
                                         "2" = "Sometimes",
                                         "2" = "Almost never,Sometimes",
                                         "3" = "Often",
                                         "3" = "Sometimes,Often",
                                         "4" = "Almost always",
                                         "4" = "Sometimes,Often,Almost always")
         ),
         T_Ang_R_3 = as.numeric(fct_recode(as_factor(Q147_8),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Almost never,Often",
                                           "4" = "Almost always")
         ),
         T_Ang_2 = as.numeric(fct_recode(as_factor(Q147_9),
                                         "1" = "Almost never",
                                         "2" = "Sometimes",
                                         "2" = "Almost never,Sometimes",
                                         "3" = "Often",
                                         "4" = "Almost always",
                                         "4" = "Often,Almost always")
         ),
         T_Ang_R_4 = as.numeric(fct_recode(as_factor(Q147_10),
                                           "1" = "Almost never",
                                           "2" = "Sometimes",
                                           "2" = "Almost never,Sometimes",
                                           "3" = "Often",
                                           "3" = "Sometimes,Often",
                                           "3" = "Almost never,Sometimes,Often",
                                           "3" = "Almost never,Often",
                                           "4" = "Almost always",
                                           "4" = "Often,Almost always")
         ),
         T_Ang_T_Total = (T_Ang_T_1 + T_Ang_T_2 + T_Ang_T_3 + T_Ang_T_4),
         T_Ang_R_Total = (T_Ang_R_1 + T_Ang_R_2 + T_Ang_R_3 + T_Ang_R_4),
         T_Ang_Total = (T_Ang_T_1 + T_Ang_T_2 + T_Ang_T_3 + T_Ang_T_4 +
                          T_Ang_R_1 + T_Ang_R_2 + T_Ang_R_3 + T_Ang_R_4 +
                          T_Ang_1 + T_Ang_2)
    );

```


## Screening Data
The following code screens the data by removing the following responses:

- Responses that did not have a current or expired/revoked full drivers license
- Responses that did not have a completed STAXI
- Responses that did not have a completed DDDI

```{r processing.screen, message=FALSE, warning=FALSE}
# Creating screened data set
screened.full <- data.full %>% 
  filter(#[Not needed] Status != "Spam", # Remove spam
         Q126...13 %in% c("Full license (current/valid)", "Full license (expired/revoked)"), # Removing responses that are not full license
         !is.na(S_Ang_Total), # Removing responses that have incomplete State Anger
         !is.na(T_Ang_Total), # Removing responses that have incomplete Trait Anger
         keep_DDDI == "TRUE") %>%  # Select only observations that have completed DDDI 
  mutate(id = row_number()) # Assign a number to each participant

screened <- screened.full[164:ncol(screened.full)] %>% # Select only variables that have been re-coded
  select(id, everything()); # Moving participant id to front of data frame
```

```{r processing.save, echo = F}
#Saving as R objects
save(data.full, file = "data/objects/data.full.Rda")
save(screened.full, file = "data/objects/screened.full.Rda")
save(screened, file = "data/objects/screened.Rda")
#save(cleaned, file = "Data/Data.frame/cleaned.Rda")
```

## Summary of Data Screened
The table below outlines how many observations did not meet any combination of the criteria laid out above.  "TRUE" means that there was a response recorded for that item.
```{r processing.summary, echo= F, message=FALSE}
bad <- anti_join(data.full, screened) %>% 
  select(Q126...13, S_Ang_Total, T_Ang_Total, DDDI_Total)
bad <- bad %>%
  mutate(License = fct_recode(as_factor(Q126...13),
                              "Full License" = "Full license (current/valid)",
                              "Full License" = "Full license (expired/revoked)",
                              "Probationary License" = "Probationary license (P-plate)",
                              "Learners License" = "Learners license (L-plate)"),
         S_Ang_Total = ifelse(!is.na(S_Ang_Total), T, NA),
         T_Ang_Total = ifelse(!is.na(T_Ang_Total), T, NA),
         DDDI_Total = ifelse(!is.na(DDDI_Total), T, NA)) %>% 
  group_by(License, S_Ang_Total, T_Ang_Total, DDDI_Total) %>% 
  summarise(
    n = n()
)

kable(bad, caption = "Table 1. Number of Observations Removed by group")
```

