# Descriptives {#Descriptives}
```{r desc.setup, include=FALSE}
library(bookdown)
library(tidyverse)
library(knitr)
library(gridExtra)
library(kableExtra)
library(table1)
library(gridExtra)

# Preparing colours for graphs
.grey <- "#A6A6A6"
.ma <- "#DC2D27"
.nma <- "#80B9C9"
.lav <- "#D9BBDC"
.lgreen <- "#BEDCB3"

# Data
load("data/objects/data.full.Rda")
load("data/objects/screened.full.Rda")
load("data/objects/screened.Rda")

# Changing NA from meth_ingest and meth_user to "No"
screened$meth_ingest[is.na(screened$meth_ingest)] <- "No"
screened$meth_user[is.na(screened$meth_user)] <- "Non-User"
screened$meth_user <- as.factor(screened$meth_user)

# Rearranging levels for education 
screened$education <- factor(screened$education, levels = c("Did not finish high school",
                                                          "High School Diploma",
                                                          "Vocational/Technical degree or certificate",
                                                          "Did not finish University",
                                                          "Bachelor Degree",
                                                          "Postgraduate Degree"))
```

***

## Demographic Summary Table
```{r desc.summary, echo = F}
x <- screened %>% mutate(ethnicity = reorder(ethnicity, ethnicity, function(x) -length(x)),
                        meth_user = reorder(meth_user, meth_user, function(x) length(x)),
                        area_live = reorder(area_live, area_live, function(x) length(x)))
label(x$age) <- "Age"
label(x$sex) <- "Sex"
label(x$meth_ingest) <- "MA Ingest"
label(x$meth_user) <- "MA User Type"
label(x$license_status) <- "License Status"
label(x$education) <- "Education"
label(x$ethnicity) <- "Ethnicity"
label(x$area_live) <- "Area of Residence"


table1(~age + sex + meth_ingest + meth_user + license_status + education + ethnicity + area_live, data = x)

```

***

## Distribution of Demographics {.tabset}

### MA Use

```{r distr.ma, echo = F}
plot.count <- screened %>%
  ggplot(aes(x = reorder(meth_user, meth_user, function(x) -length(x)))) +
  geom_bar(fill = .grey, col = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -.3) +
  labs(x = "Type of User", y = "n") +
  ggtitle("Count of MA and non-MA users") +
  theme_light()

plot.count
```

***

### Sex
```{r distr.sex, echo = F}
bar.sex <- screened %>% 
  ggplot(aes(x = sex, fill = sex)) +
  geom_bar(col = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -.3) +
  labs(x = "Sex", y = "") +
  ggtitle("Sex Count") +
  theme_light() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.lav, .lgreen))

bar.sex.ma <- screened %>%
  ggplot(aes(x = sex, fill = meth_ingest)) +
  geom_bar(col = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -.3) +
  labs(x = "Sex", y = "n") +
  ggtitle("Sex count by MA use") +
  theme_light() +
  theme(legend.position = "none") +
  facet_wrap(~ meth_ingest) +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(bar.sex, bar.sex.ma, nrow = 1)

```

***

### Age
```{r distr.age, echo = F}
# Histogram age
hist.age <- screened %>% 
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 2, col = "black", fill = .grey) +
  labs(x = "Age", y = "") +
  #ggtitle("Distribution of Age") +
  theme_light()

#Histogram of age by MA
hist.age.ma <- screened %>%
  ggplot(aes(x = age, fill = meth_ingest)) +
  geom_histogram(binwidth = 1, col = "black") +
  labs(x = "Age", y = "", fill = "MA Use") +
  #ggtitle("Distribution of Age by MA use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  scale_fill_manual(values = c(.ma, .nma))

# Density plot of age by MA
dens.age.ma <- screened %>% 
  ggplot(aes(x = age, fill = meth_ingest)) +
  geom_density(alpha = 0.5) +
  labs(x = "Age", y = "Density", fill = "MA Use") +
  #ggtitle("Distribution of Age by MA use (Density)") +
  theme_light() +
  scale_fill_manual(values = c(.ma, .nma))

# Boxplot of age by MA
box.age.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y =  age, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  scale_fill_manual(values = c(.ma, .nma)) +
  geom_jitter(alpha = 0.5, width = 0.08) +
  theme_light() +
  theme(legend.position = "none") +
  labs(x = "MA Use", y = "Age");
  #ggtitle("Distribution of Age by MA use")

grid.arrange(hist.age, hist.age.ma, dens.age.ma, box.age.ma, top = "Distribution of Age by MA Use")
```

***

### Education
```{r distr.edu, echo = F}
bar.edu <- screened %>% 
  mutate(education = fct_reorder(education, desc(education))) %>% 
  ggplot(aes(x = education)) +
  geom_bar(col = "black", fill = .grey) +
  coord_flip() +
  labs(x = "Education Level", y = "") +
  #ggtitle("Education Count") +
  theme_light()

bar.edu.ma <- screened %>%
  mutate(education = fct_reorder(education, desc(education))) %>% # Reorder levels of education 
  ggplot(aes(x = education, fill = meth_ingest)) +
  geom_bar(position = "dodge", col = "black") +
  #geom_text(stat = "count", aes(label = ..count..)) +
  coord_flip() +
  labs(x = "Education Level", y = "", fill = "MA Use") +
  #ggtitle("Education count by MA use") +
  theme_light() +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(bar.edu, bar.edu.ma, nrow = 2, top = "Education Distribution")
```

***

### Ethnicity
```{r distr.eth, echo = F}
bar.eth <- screened %>% 
  ggplot(aes(x = reorder(ethnicity, ethnicity, function(x) -length(x)))) +
  geom_bar(fill = .grey, col = "black") +
  geom_text(stat = "count", aes(label = ..count..), hjust = -.3) +
  coord_flip() +
  labs(x = "Ethnicity", y = "") +
  theme_light()

bar.eth.ma <- screened %>%
  ggplot(aes(x = reorder(ethnicity, ethnicity, function(x) -length(x)), fill = meth_ingest)) +
  geom_bar(col = "black", position = "dodge") +
  coord_flip() +
  labs(x = "Ethnicity", y = "", fill = "MA Use") +
  theme_light() +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(bar.eth, bar.eth.ma, nrow = 2, top = "Ethnicity Distribution")
```

***

### Area of Residence
```{r distr.live, echo = F}
bar.res <- screened %>% 
  ggplot(aes(x = reorder(area_live, area_live, function(x) length(x)))) +
  geom_bar(fill = .grey, col = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -.3) +
  labs(x = "Area of Residence", y = "") +
  theme_light()

bar.res.ma <- screened %>% 
  ggplot(aes(x = reorder(area_live, area_live, function(x) length(x)), fill = meth_ingest)) +
  geom_bar(col = "black", position = "dodge") +
  labs(x = "Area of Residence", fill = "MA Use") +
  scale_fill_manual(values = c(.ma, .nma)) +
  theme_light();

grid.arrange(bar.res, bar.res.ma, nrow = 2, top = "Area of Residence Distribution")

```

***

## Bivariate distribution of key variables 
### Dula Dangerous Driving Index (DDDI) {.tabset}
#### About
The DDDI includes 28$^*$ items (divided into 3 categorical subscales) with each item assessing a persons tendency to engage in certain driving practices or beliefs held around specific driving behaviours.  Each item is scored on a 5-point Likert scale from 1 (Never) to 5 (Always).

<br>

The total score can be used as a composite measure for one's tendency and/or willingness to engage in dangerous driving.  Scores can range from 27 to 135.

<br>

##### Subscales:

**Aggressive Driving:**
Assessed with 7 items which reflect behaviours that are intentionally meant to annoy, irritate or punish other drivers.  E.g. *I flash my headlights when I am annoyed by another driver.*

Scores range from 7 to 35.

<br>

**Negative Emotional Driving:**
Assessed with 9 items which gauge irritability and anger while driving and the tendency to become annoyed with other drivers.  E.g. *I lose my temper while driving.*

Scores range from 9 to 45.

<br>

**Risky Driving:**
Assessed with 11 items which gauge ones willingness to engage in unsafe driving behaviours.  E.g. *I will "drag race" other drivers at stop lights to get out front.*

Scores range from 11 to 55. 

<br>
<br>

$^*$The present study used 27 items with one item from the "Risky Driving" subscale - *I will weave in and out of slower traffic* - omitted from the questionnaire. 

***

#### Total Score
```{r di.total, echo = F}
# Summary Table

# Histogram
hist.di <- screened %>% 
  ggplot(aes(x = DDDI_Total)) +
  geom_histogram(binwidth = 3, col = "black", fill = .grey) +
  labs(x = "DDDI Total Score", y = "") +
  theme_light()

# Hist by MA
hist.di.ma <- screened %>% 
  ggplot(aes(x = DDDI_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 3, col = "black") +
  labs(x = "DDDI Total Score", y = "", fill = "MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.di.ma <- screened %>% 
  ggplot(aes(x = DDDI_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "DDDI Total Score", y = "Density", fill = "MA Use") +
  theme_light()

# Box and scatter
box.di.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = DDDI_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "DDDI Total") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.di, hist.di.ma, dens.di.ma, box.di.ma, nrow = 2, ncol = 2, top = "Distribution of Total DDDI Scores")

```

***

#### Aggressive Driving
```{r di.AG, echo = F}
# Histogram
hist.ag <- screened %>% 
  ggplot(aes(x = DDDI_AD_Total)) +
  geom_histogram(binwidth = 2, col = "black", fill = .grey) +
  labs(x = "DDDI Aggression Score", y = "") +
  #ggtitle("Distribution of DDDI Total Score") +
  theme_light()

# Hist by MA
hist.ag.ma <- screened %>% 
  ggplot(aes(x = DDDI_AD_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 2, col = "black") +
  labs(x = "DDDI Aggression Score", y = "", fill = "MA Use") +
  #ggtitle("DDDI Aggression by MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.ag.ma <- screened %>% 
  ggplot(aes(x = DDDI_AD_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "DDDI Aggression Score", y = "Density", fill = "MA Use") +
  #ggtitle("DDDI Aggression by MA Use (Density)") +
  theme_light()

# Box and scatter
box.ag.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = DDDI_AD_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "DDDI Aggression") +
  #ggtitle("Box plot of DDDI Aggression by MA Use") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.ag, hist.ag.ma, dens.ag.ma, box.ag.ma, nrow = 2, top = "Distribution of DDDI Aggressive Driving Scores")
```

***

#### Negative Emotional Driving
```{r di.NE, echo = F}
# Histogram
hist.ned <- screened %>% 
  ggplot(aes(x = DDDI_NE_Total)) +
  geom_histogram(binwidth = 2, col = "black", fill = .grey) +
  labs(x = "DDDI NED Score", y = "") +
  #ggtitle("Distribution of DDDI Negative Emotional Driving (NED) Score") +
  theme_light()

# Hist by MA
hist.ned.ma <- screened %>% 
  ggplot(aes(x = DDDI_NE_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 2, col = "black") +
  labs(x = "DDDI NED Score", y = "", fill = "MA Use") +
  #ggtitle("DDDI NED by MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.ned.ma <- screened %>% 
  ggplot(aes(x = DDDI_NE_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "DDDI NED Score", y = "Density", fill = "MA Use") +
  #ggtitle("DDDI NED by MA Use (Density)") +
  theme_light()

# Box and scatter
box.ned.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = DDDI_NE_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "DDDI NED") +
  #ggtitle("Box plot of DDDI NED by MA Use") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.ned, hist.ned.ma, dens.ned.ma, box.ned.ma, nrow = 2, top = "Distribution of DDDI Negative Emotional Driving Scores")

```

***

#### Risky Driving
```{r di.RD, echo = F}
# Histogram
hist.rd <- screened %>% 
  ggplot(aes(x = DDDI_RD_Total)) +
  geom_histogram(binwidth = 2, col = "black", fill = .grey) +
  labs(x = "DDDI Risky Driving Score", y = "") +
  #ggtitle("Distribution of DDDI Risky Driving Score") +
  theme_light()

# Hist by MA
hist.rd.ma <- screened %>% 
  ggplot(aes(x = DDDI_RD_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 2, col = "black") +
  labs(x = "DDDI Risky Driving Score", y = "", fill = "MA Use") +
  #ggtitle("DDDI Risky Driving by MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.rd.ma <- screened %>% 
  ggplot(aes(x = DDDI_RD_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "DDDI Risky Driving Score", y = "Density", fill = "MA Use") +
  #ggtitle("DDDI Risky Driving by MA Use (Density)") +
  theme_light()

# Box and scatter
box.rd.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = DDDI_RD_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "DDDI Risky Driving") +
  #ggtitle("Box plot of DDDI Risky Driving by MA Use") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.rd, hist.rd.ma, dens.rd.ma, box.rd.ma, nrow = 2, top = "Distribution of DDDI Risky Driving Scores")

```

***

### STAXI-2 {.tabset}
#### About
The State-Trait Anger Expression Inventory (STAXI-2) is designed to understand the attitudes, emotional states and behaviours that are typical to a person in regard to their feelings, control and expression of anger.  It distinguishes anger between being a passing/present state as a personality trait.

*Description of scoring*

##### State Anger
Assesses the intensity of the individual's angry feelings at time of testing.

##### Subscales:
**Feeling Angry (S-Ang/F):**
TBC

<br>

**Feel like verbally expressing anger (S-Ang/V):**
TBC

<br>

**Feel like physically expressing anger (A-Ang/P):**
TBC

***

#### State Anger Total
```{r staxi.state, echo = F}
# Histogram
hist.sstaxi <- screened %>% 
  ggplot(aes(x = S_Ang_Total)) +
  geom_histogram(binwidth = 1, col = "black", fill = .grey) +
  labs(x = "State Anger", y = "") +
  #ggtitle("Distribution of State Anger Scores") +
  theme_light()

# Hist by MA
hist.sstaxi.ma <- screened %>% 
  ggplot(aes(x = S_Ang_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 1, col = "black") +
  labs(x = "State Anger", y = "", fill = "MA Use") +
  #ggtitle("State Anger by MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.sstaxi.ma <- screened %>% 
  ggplot(aes(x = S_Ang_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "State Anger", y = "Density", fill = "MA Use") +
  #ggtitle("State Anger by MA Use (Density)") +
  theme_light()

# Box and scatter
box.sstaxi.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = S_Ang_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "State Anger") +
  #ggtitle("Box plot of State Anger by MA Use") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.sstaxi, hist.sstaxi.ma, dens.sstaxi.ma, box.sstaxi.ma, ncol = 2, top = "Distribution of State STAXI Scores (Total)")
```

***

#### Trait Anger Total
```{r staxi.trait, echo = F}
# Histogram
hist.tstaxi <- screened %>% 
  ggplot(aes(x = T_Ang_Total)) +
  geom_histogram(binwidth = 1, col = "black", fill = .grey) +
  labs(x = "Trait Anger", y = "") +
  #ggtitle("Distribution of Trait Anger Scores") +
  theme_light()

# Hist by MA
hist.tstaxi.ma <- screened %>% 
  ggplot(aes(x = T_Ang_Total, fill = meth_ingest)) +
  geom_histogram(binwidth = 1, col = "black") +
  labs(x = "Trait Anger", y = "", fill = "MA Use") +
  #ggtitle("Trait Anger by MA Use") +
  theme_light() +
  facet_grid(meth_ingest ~.) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

# Dens by MA
dens.tstaxi.ma <- screened %>% 
  ggplot(aes(x = T_Ang_Total, fill = meth_ingest)) +
  geom_density(col = "black", alpha = 0.5) +
  scale_fill_manual(values = c(.ma, .nma)) +
  labs(x = "Trait Anger", y = "Density", fill = "MA Use") +
  #ggtitle("Trait Anger by MA Use (Density)") +
  theme_light()

# Box and scatter
box.tstaxi.ma <- screened %>% 
  ggplot(aes(x = meth_ingest, y = T_Ang_Total, fill = meth_ingest)) +
  geom_boxplot(outlier.alpha = 0) +
  geom_jitter(width = 0.08, alpha = 0.5) +
  theme_light() +
  labs(x = "MA Use", y = "Trait Anger") +
  #ggtitle("Box plot of Trait Anger by MA Use") +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(.ma, .nma))

grid.arrange(hist.tstaxi, hist.tstaxi.ma, dens.tstaxi.ma, box.tstaxi.ma, ncol = 2, top = "Distribution of Trait Staxi Scores (Total)")

```

***
