# Additional Analyses
```{r additional.lib, include=F}
library(bookdown)
library(tidyverse)
library(apaTables)
library(gridExtra)
library(table1)
library(kableExtra)
library(car) #VIF
```

```{r data.load.add, include = F}
load("data/objects/screened.full.Rda")
load("data/objects/screened.Rda")
```

```{r data.preparation.add, include = F}
# Preparing colours for graphs
.grey <- "#A6A6A6"
.ma <- "#DC2D27"
.nma <- "#39B9FF"
.lav <- "#D9BBDC"
.lgreen <- "#BEDCB3"

# Changing NA from meth_ingest and meth_user to "No"
screened$meth_ingest[is.na(screened$meth_ingest)] <- "No"
screened$meth_user[is.na(screened$meth_user)] <- "Non-User"
screened$meth_user <- as.factor(screened$meth_user)

# Rearranging levels for education 
screened$education <- factor(screened$education, levels = c("Did not finish high school",
                                                          "High School Diploma",
                                                          "Vocational/Technical degree or certificate",
                                                          "Did not finish University",
                                                          "Bachelor Degree",
                                                          "Postgraduate Degree"))

# Filtering for MA only
ma <- screened %>% filter(meth_ingest == "Yes")

# Converting non-drinkers to 0 on AUDIT-C
ma <- ma %>% 
  mutate(AUDIT_Total = ifelse(is.na(AUDIT_Total), 0, AUDIT_Total))

options(scipen = 999) # Removing scientific notation
```

## Not Forced Entry
### Model Building
```{r not-forced}
m0 <- lm(DDDI_Total~1, data = ma) # Total SS
m1 <- lm(DDDI_Total ~ age + sex, data = ma)
m2.rm <- lm(DDDI_Total ~ age + AUDIT_Total + meth_SDS, data = ma)
m3.rm <- lm(DDDI_Total ~ AUDIT_Total + meth_SDS + T_Ang_Total, data = ma)
```

### Sums of Suares
#### Total SS {-}
```{r total.ss.step, echo=F}
anova(m0) %>% kable(align = "c") %>% kable_styling()
```

#### Model SS {-}
```{r model.ss.step, echo=F}
anova(m1, m2.rm, m3.rm) %>% kable(align = "c") %>% kable_styling()
```
### Model Summaries
#### Model 1 {-}
```{r, echo = F}
summary(m1)
```

#### Model 2 {-}
```{r, echo=F}
summary(m2.rm)
```

#### Model 3 {-}
```{r, echo=F}
summary(m3.rm)
```

### Assumptions
#### Plot of Residuals {-}
```{r, echo=F}
std.res <- rstandard(m3.rm)
m3.rm.std.res <- tibble(
  Std.Res = std.res,
  Fitted = m3.rm$fitted.values
)

m3.rm.std.res %>% 
  ggplot(aes(x = Fitted, y = Std.Res)) +
  geom_point() +
  geom_hline(aes(yintercept = 0), linetype = "dashed", alpha = 0.5) +
  theme_light() +
  labs(x = "Fitted", y = "Standardised Residuals") +
  ggtitle("Plot of Residuals")
```

#### Colinearity {-}
```{r, echo=F}
tibble(Variable = c("AUDIT-C", "SDS", "STAXI-T"),
       VIF = vif(m3.rm))
```

#### Homogeneity {-]
```{r ass.homo.rm, echo=F}
plot(m3.rm,1)
```

#### Linearity {-}
```{r ass.lin.rm, echo=F}
plot(m3.rm, 5)
```

#### Normality of Residuals {-}
```{r ass.norm.rm, echo=F}
plot(m3.rm, 2)
```

#### Outliers {-}
##### Residuals {-}
```{r ass.res.std.dev, echo=F}
ma %>% 
  ggplot(aes(x = as.numeric(row.names(ma)), y = std.res)) +
  geom_point() +
  geom_hline(aes(yintercept = 2), linetype = "dashed", alpha = 0.5) +
  geom_hline(aes(yintercept = -2), linetype = "dashed", alpha = 0.5) +
  geom_text(size = 3,
            label = as.numeric(row.names(ma)),
            nudge_x = 0.25,
            nudge_y = 0.25,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Std Residuals") +
  ggtitle("Std. Residual by Index")
```

##### Cooks D {-}
```{r cooks.doodle, echo=F}
# Calculate Cook's D for each observation
cooksD <- cooks.distance(m3.rm)

# Plot Cook's D
n <- nrow(ma)

ma %>% 
  ggplot(aes(x = as.numeric(row.names(ma)), y = cooksD)) +
  geom_point() +
  geom_hline(yintercept = 4/n, linetype = "dashed") +
  geom_text(size = 2.5,
            label = as.numeric(row.names(ma)),
            nudge_y = 0.025,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Cooks Distance") +
  ggtitle("Cooks Distance")
```

##### Mahalanobis Distance {-}
```{r mahalinobis.rm, echo=F}
ma.key <- ma %>% 
  select(AUDIT_Total, meth_SDS, T_Ang_Total)

# Calculate mahalanobis distance
ma.key$mahal <- mahalanobis(ma.key, colMeans(ma.key), cov(ma.key))

# p-value for mahalanobis
ma.key$p <- pchisq(ma.key$mahal, df = 2, lower.tail = FALSE)

# tibble(
#   index = which(ma.key$p < .05),
#   mahal = ma.key$mahal[which(ma.key$p < .05)],
#   p = ma.key$p[which(ma.key$p < .05)]
# ) %>% kable(caption = "Mahalanobis < .05", align = "c") %>% kable_styling()
 
# Create a plotty plot
ma.key %>% 
  ggplot(aes(x = as.numeric(row.names(ma.key)), y = mahal, col = p < .05)) +
  geom_point() +
  geom_text(size = 2.5,
            label = as.numeric(row.names(ma)),
            nudge_y = 0.3,
            check_overlap = T) +
  scale_color_manual(values = c("black", "red")) +
  theme_light() +
  labs(x = "Index", y = "Mahalanobis Distance") +
  ggtitle("Mahalanobis Distance Plot")
```


## Removed Outlier (Forced Entry)
**Omitting response 146**

```{r outlier.prep, include=F}
# Create column to easily remove rows
ma <- ma %>% 
  mutate(include = TRUE)
```

### Model Building
```{r buil.models.2}
ma.nout <- ma %>% mutate(include = ifelse(id == 146, FALSE, TRUE)) # Not including id 146

m0.2 <- lm(DDDI_Total~1, data = ma.nout[ma.nout$include == TRUE, ]) # Total SS
m1.2 <- lm(DDDI_Total~age + sex, data = ma.nout[ma.nout$include == TRUE, ]) # Model 1 (demographics)
m2.2 <- lm(DDDI_Total~age + sex + AUDIT_Total + meth_SDS, data = ma.nout[ma.nout$include == TRUE, ]) # Alcohol and MA use characteristics
m3.2 <- lm(DDDI_Total~age + sex + AUDIT_Total + meth_SDS + T_Ang_Total, data = ma.nout[ma.nout$include == TRUE, ]) # STAXI
```

### Sums of Squares
#### Total SS {-}
```{r ss.m0.2, echo=F}
anova(m0.2) %>% kable() %>% kable_styling()
```

#### Model SS {-}
```{r ss.models.2, echo=F}
anova(m1.2, m2.2, m3.2) %>% kable(align = "c") %>% kable_styling()
```
The model with Alcohol and SDS accounts for an additional 3088.06 Sum of Squares over and above the model including age and gender and this change was statistically significant (p < .01).  The $R^2$ increased by 24.6% in model 2.  

The model with Trait Anger accounts for an additional 1823.60 Sum of Squares controlling for demographics and alcohol/substance use and this too was statistically significant (p < .01).  The $R^2$ increased by 14.6%.  

### Model Summaries
#### Model 1 {-}
```{r model.sum.2, echo=F}
options(scipen = 999)
summary(m1.2)
```

#### Model 2 {-}
```{r model.2.2, echo=F}
summary(m2.2)
```

#### Model 3 {-}
```{r model.3.2, echo=F}
summary(m3.2)
```

### Assumptions
#### Plot of Residuals {-}
```{r resid.plot.2, echo=F}
std.res.2 <- rstandard(m3.2)

m3.2.std.res <- tibble(
  Std.Res = std.res.2,
  Fitted = m3.2$fitted.values
)

m3.2.std.res %>% 
  ggplot(aes(x = Fitted, y = Std.Res)) +
  geom_point() +
  geom_hline(aes(yintercept = 0), linetype = "dashed", alpha = 0.5) +
  theme_light() +
  labs(x = "Fitted", y = "Standardised Residuals") +
  ggtitle("Plot of Residuals")

```

#### Colinearity (model 3) {-}
```{r}
tibble(Variable = c("Age", "Sex", "AUDIT-C", "SDS", "STAXI-T"),
       VIF = vif(m3.2))
```

#### Homogeneity {-}
```{r ass.homo.2, echo = F}
plot(m3.2, 1)
```

#### Linearity {-}

```{r ass.lin.2, echo=F}
plot(m3.2, 5)
```



#### Normality of Residuals {-}
```{r ass.norm.2, echo=F}
plot(m3.2, 2)
```

#### Outliers {-}
##### Residuals {-}
```{r ass.out.2, echo=F}
# Residuals by index
ma.nout[ma.nout$include == TRUE, ] %>% 
  ggplot(aes(x = as.numeric(row.names(ma.nout[ma.nout$include == TRUE, ])), y = std.res.2)) +
  geom_point() +
  geom_hline(aes(yintercept = 2), linetype = "dashed", alpha = 0.5) +
  geom_hline(aes(yintercept = -2), linetype = "dashed", alpha = 0.5) +
  geom_text(size = 3,
            label = as.numeric(row.names(ma.nout[ma.nout$include == TRUE,])),
            nudge_x = 0.25,
            nudge_y = 0.25,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Std Residuals") +
  ggtitle("Std. Residual by Index")
```

##### Cooks D {-}
```{r cooks.d.2, echo=F}
# Calculate Cook's D for each observation
cooksD <- cooks.distance(m3.2)

# Plot Cook's D
n <- nrow(ma.nout[ma.nout$include == TRUE,])

ma.nout[ma.nout$include == TRUE,] %>% 
  ggplot(aes(x = as.numeric(row.names(ma.nout[ma.nout$include == TRUE,])), y = cooksD)) +
  geom_point() +
  geom_hline(yintercept = 4/n, linetype = "dashed") +
  geom_text(size = 2.5,
            label = as.numeric(row.names(ma.nout[ma.nout$include == TRUE,])),
            nudge_y = 0.01,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Cooks Distance") +
  ggtitle("Cooks Distance")
```

##### Mahalanobis Distance {-}
```{r mahalanobis.2, echo=F}
ma.key.nout <- ma.nout[ma.nout$include == TRUE, ] %>% 
  select(age, sex, AUDIT_Total, meth_SDS, T_Ang_Total)

ma.key.nout <- ma.key.nout %>% 
  mutate(sex = ifelse(ma.key.nout$sex == "Male", 1, 0)) # Converting sex to numeric for calculations

# Calculate mahalanobis distance
ma.key.nout$mahal <- mahalanobis(ma.key.nout, colMeans(ma.key.nout), cov(ma.key.nout))


# p-value for mahalanobis
ma.key.nout$p <- pchisq(ma.key.nout$mahal, df = 4, lower.tail = FALSE)

tibble(
  index = which(ma.key.nout$p < .05),
  # id = which(ma.nout$id[which(ma.key.nout$p < .05),])
  mahal = ma.key.nout$mahal[which(ma.key.nout$p < .05)],
  p = ma.key.nout$p[which(ma.key.nout$p < .05)]
) %>% kable(caption = "Mahalanobis < .01", align = "c") %>% kable_styling()
 
# Create a plotty plot
ma.key.nout %>% 
  ggplot(aes(x = as.numeric(row.names(ma.key.nout)), y = mahal, col = p < .05)) +
  geom_point() +
  scale_color_manual(values = c("black", "red")) +
  theme_light() +
  labs(x = "Index", y = "Mahalanobis Distance") +
  ggtitle("Mahalanobis Distance Plot")

```

## Removed Outlier (Not Forced Entry)
### Model Building
```{r nout.step}
ma.nout <- ma %>% filter(id != 146) # Not including id 146

m0.3 <- lm(DDDI_Total~1, data = ma.nout) # Total SS
m1.3 <- lm(DDDI_Total~age + sex, data = ma.nout) # Model 1 (demographics)
m2.3 <- lm(DDDI_Total~age + AUDIT_Total + meth_SDS, data = ma.nout) # Alcohol and MA use characteristics
m3.3 <- lm(DDDI_Total~AUDIT_Total + meth_SDS + T_Ang_Total, data = ma.nout) # STAXI
```

### Sums of Squares
#### Total SS {-}
```{r nout.step.ss, echo=F}
anova(m0.3) %>% kable(align = "c") %>% kable_styling()
```

#### Model SS {-}
```{r nout.step.ssm, echo=F}
anova(m1.3, m2.3, m3.3) %>% kable(align = "c") %>% kable_styling()
```
### Model Summaries
#### Model 1 {-}
```{r nout.sum.1, echo=F}
summary(m1.3)
```

#### Model 2{-}
```{r nout.sum.2, echo=F}
summary(m2.3)
```

#### Model 3 {-}
```{r nout.sum.3, echo=F}
summary(m3.3)
```
### Assumptions
#### Plot of Residuals {-}
```{r nout.resid, echo=F}
std.res.3 <- rstandard(m3.3)

m3.3.std.res <- tibble(
  Std.Res = std.res.3,
  Fitted = m3.3$fitted.values
)

m3.3.std.res %>% 
  ggplot(aes(x = Fitted, y = Std.Res)) +
  geom_point() +
  geom_hline(aes(yintercept = 0), linetype = "dashed", alpha = 0.5) +
  theme_light() +
  labs(x = "Fitted", y = "Standardised Residuals") +
  ggtitle("Plot of Residuals")
```
#### Colinearity {-}
```{r nout.colin, echo=F}
tibble(
  Variable = c("AUDIT-C", "SDS", "STAXI-T"),
  VIF = vif(m3.3)
)
```

#### Homogeneity {-}
```{r nout.homo, echo=F}
plot(m3.3, 1)
```

#### Linearity {-}

```{r ass.lin.3, echo=F}
plot(m3.3, 5)
```



#### Normality of Residuals {-}
```{r ass.norm.3, echo=F}
plot(m3.3, 2)

shapiro.test(m3.3$residuals)
```

#### Outliers {-}
##### Residuals {-}
```{r ass.out.3, echo=F}
# Residuals by index
ma.nout %>% 
  ggplot(aes(x = as.numeric(row.names(ma.nout)), y = std.res.3)) +
  geom_point() +
  geom_hline(aes(yintercept = 2), linetype = "dashed", alpha = 0.5) +
  geom_hline(aes(yintercept = -2), linetype = "dashed", alpha = 0.5) +
  geom_text(size = 3,
            label = as.numeric(row.names(ma.nout)),
            nudge_x = 0.25,
            nudge_y = 0.25,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Std Residuals") +
  ggtitle("Std. Residual by Index")
```

##### Cooks D {-}
```{r cooks.d.3, echo=F}
# Calculate Cook's D for each observation
cooksD <- cooks.distance(m3.3)

# Plot Cook's D
n <- nrow(ma.nout)

ma.nout %>% 
  ggplot(aes(x = as.numeric(row.names(ma.nout)), y = cooksD)) +
  geom_point() +
  geom_hline(yintercept = 4/n, linetype = "dashed") +
  geom_text(size = 2.5,
            label = as.numeric(row.names(ma.nout)),
            nudge_y = 0.01,
            check_overlap = T) +
  theme_light() +
  labs(x = "Index", y = "Cooks Distance") +
  ggtitle("Cooks Distance")
```







