# Appendix

```{r appendix.packages, include=F}
library(tidyverse)
library(knitr)
library(kableExtra)
```

## Attitudes Questionnaire
### Attitudes towards drink driving
Ten statements regarding the tolerance of participants toward drink driving behaviour,
formed the body of this measure. Participants were asked to rate whether they agreed or
disagreed with the statements on a 7‐point Likert scale (from “strongly agree” = 1 to “strongly
disagree” = 7). The mean score on all ten statements will be calculated after reverse scoring
of negatively worded items to give an attitude toward drink driving rating, which range from
1 “unfavourable attitude to drink driving” to 7 “favourable attitude to drink driving.”

1. Most of my friends think its ok to drink and drive
2. It's ok to drive after drinking as long as you're not too drunk
3. People who take drink and drive should go to jail
4. My community needs stricter laws against drink driving
5. The police aren't tough enough on drink drivers
6. It's ok to drink‐drive as long as you don't get caught
7. Everybody who drinks alcohol, drives under their influence once in a while
8. My friends would think I was dumb if I drove after drinking alcohol
9. The dangers of drink‐driving are overrated
10. People who drink and drive should lose their driver’s license


### Attitudes towards drug driving

1. Most of my friends think its ok to take drugs and drive
2. It's ok to drive after taking drugs as long as you're not too high
3. People who take drugs and drive should go to jail
4. My community needs stricter laws against drug driving
5. The police aren't tough enough on drug drivers
6. It's ok to drug drive as long as you don't get caught
7. Everybody who takes drugs, drives under their influence once in a while
8. My friends would think I was dumb if I drove after taking drugs
9. The dangers of drug driving are overrated
10. People who take drugs and drive should lose their driver’s license

## Dula Danderous Driving Index (DDDI)
The following Table demonstrates all the DDDI items (and their respective subscales) that were used for the present study:

```{r DDDI, echo=F}
di.qs <- read_csv("data/dddi.csv", col_names = FALSE)

di.clean <- str_remove_all(di.qs$X1, "\\d{1,2}\\.?\\s?\\d?\\.?\\s?")

subscale <- str_extract(di.clean, "[A-Z]{2}")
item <- str_remove(di.clean, "\\([A-Z]{2}\\)") %>% str_trim

dddi <- tibble(
  item = item,
  subscale = subscale
) %>% arrange(subscale)



kable(dddi) %>% kable_classic() %>% scroll_box()

```
